### 2016-07-27 main.tex
Most of the rest of reviewer feedback:
- Clarify inclusion of non-song data in training/test

- Remove apparently-confusing (?!) reference to hillclimbing

- Clarify how we measure latency, jitter, and give example of how to trigger at the very beginning of a syllable?

- "Here's a presentation of one bird; we have run others with similar results."  Ok?

- Quick reference to why this might work with Bengalese finches (correct me?)

- Remove the rest of Jeff's experiment.

Still waiting on new accuracy data, and confirmation that Levenberg-Marquardt is obsolete.

With inputs well outside the space on which a neural network has been
trained, its outputs will be essentially random. In order to reduce
the false positive rate it is necessary to provide negative training
examples that include silence, cage noise, wing flapping, non-song
vocalisations, and perhaps songs from other birds.  Although it will
depend on the makeup of the non-song data, we have found that training
with as low as a 1:1 ratio of non-song to song yields excellent
results on most birds.

@@

\subsubsection{Computing optimal output thresholds}
\label{sec:optimalthresholds}
After the network is trained, outputs of the network for any input are
now available, and will be in (or, due to noisy inputs and imperfect
training, close to) the interval (0, 1). We must choose a threshold
above which the output is considered a positive detection. Finding the
optimal threshold requires two choices. The first is the relative cost
of false negatives to false positives, $C_n$. The second is the
acceptable time interval: if the true event occurs at time $t$, and
the detector triggers at any time $t\pm\Delta t$, then it is
considered a correct detection. Then the optimal detection threshold
is the number that minimises $\textrm{[false positives]}
+C_n\cdot\textrm{[false negatives]}$ over the training set, using the
definitions of false positives and negatives given in
Section~\ref{sec:accuracy}. Since large portions of the cost function
are flat, hillclimbing is ineffective.  Random-restart hillclimbing
would work, but a brute-force search requires fractions of a
second. For the results presented here, we have used $C_n=1$ and
$\Delta t=10$ ms.

@@

We define the accuracy of the network based on its classification
performance per frame. In order to avoid the apparent problem of every
non-detected non-syllable counting as a true negative, we also tried
defining accuracy on a per-song basis, such that a song without the
target syllable counted as a single true negative.  Computing the
optimal output thresholds on a per-frame basis resulted in higher
thresholds and thus a lower false-positive rate, with minimal
consequences to the false-negative rate, while also providing a valid
definition of false-positive rate for data streams that had not been
segmented into songs.

@@

We evaluate the time taken from the presentation of the target
syllable to the firing of the detector's TTL pulse. While playing the
audio test file from any audio playback device, the TTL output from
the ground-truth channel of the audio output may be used as the
trigger pulse for an oscilloscope, and compared to the TTL pulse
produced by the detector implementation, which sees only the birdsong
channel of the audio file. For this purpose we used a pulse generator
(Philips PM 5715, with a listed latency of 50 ns, jitter of $\leq
0.1\%$ or 50 ps, whichever is greater) to widen the detector's output
spike to a number much larger than the jitter ($\sim 100$ ms).  This
obviates pulse length variability in the output device by essentially
discarding the falling edge of the output pulse.  The oscilloscope is
then set to averaging mode (128-trigger average) in order to collect
timing data. The canonical signal is the trigger at $t=0$, and the
average of the detector's detection events will be seen as a
low-to-high transition with form approximating the cumulative
probability distribution function (CDF) of the detector's output in
response to the chosen song event, with individual detection events visible as steps in this curve.

% Use to say: "Mean latency is then given as the halfway point of that detection 
% sigmoid."
%
% I don't think this description matches the calculation, this description
% seems to better match a "median" latency. The mean latency is calculated
% as an average latency of all detection events, which is the same as 
% fitting a normal distribution to the detection events and taking the mean
% of the normal distribution (the MLE estimator is the same as the sample mean).

Mean latency is then given as the average time between the 
canonical signal and the corresponding detection event. 
It is a helpful number, but not a critical one, since a
detector with high but constant latency can often be trained to
trigger at a point somewhat before the true moment of interest,
especially given the stereotypy of zebra finch song.  Often more
important is latency jitter: how much variability is there in the
latency?  We define jitter as the standard deviation of the latency.

@@

We have used this detector for song alignment and feedback experiments
in 5 behaving birds, and for offline analysis on various others.  For
simplicity we present performance on 6 randomly chosen points in one
bird's song, but the results presented here are representative of
real-world performance.\marginpar{Ok?}

@@

\subsection{Fibre Photometry}
\label{sec:fp-results}

\fig{fig:fp-audio} shows 1,123 song performances from a single bird. 
At trial 858, the altered auditory feedback (AAF) was introduced, 
triggered by the first syllable in the song.

Measurements of the fluorescence from genetically encoded calcium indicators
in the HVC shelf reveal an AAF-sensitive response as compared with catch trials
(\fig{fig:fp-results}). This suggests a population of cells in the HVC
shelf that respond to AAF and may be involved in error signaling, given projections
from the shelf to AIV, an area area known to be critical for processing of 
sensory errors during singing \cite{MandelblatCerf:2014eu}.

The neural-network-based syllable detector enabled this experiment
by allowing low-latency AAF triggered off user-selected syllables, 
without hand-tuning and without relying on harmonic stacks needed 
for filter-bank-based syllable detection. The detector will allow
continued research into the neural encoding of these error signals.

\begin{figure}
  \begin{center}
    \includegraphics[width=7cm]{Fig8}
  \end{center}
  \caption{Audio amplitude stack plot of the experiment as aligned by
    the bird's song.  The top panel shows a spectrogram of the song
    with the triggered white-noise stimulus.  In the bottom panel,
    each row is average amplitude for a single performance of the song
    (1123 songs total).  The white-noise stimulus is visible as a
    bright yellow region after the first syllable in the final quarter
    of the trials.}
  \label{fig:fp-audio}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=7cm]{Fig9}
  \end{center}
  \caption{Fibre photometry during AAF reveals an AAF-sensitive response
  (lines indicate mean, shading indicates 95\% confidence interval, bootstrap).
  Blue are catch trials, red are AAF trials.}
  \label{fig:fp-results}
\end{figure}

@@

This syllable detector is appropriate for zebra finch song, and
although our tests were carried out on songs from that species, it is
also likely to work well for Bengalese finches.  It offers the
following benefits:
\begin{itemize}
\item The detector is accurate. False negative and false positive
  rates can be well under 0.5\% and 0.01\% respectively, and trading
  these two numbers off against each other is through a single
  relative-cost parameter.
\item Latency is generally under a millisecond, with jitter around 2
  ms.
\item Works on a wide range of target syllables using the default
  values described here, generally eliminating the need for
  hand-tuning.
\item Runs fast enough for syllable-modification experiments on
  inexpensive consumer-grade hardware, although we recommend that the
  training phase be run on a fast desktop system with 32 GB of RAM.
\item A single detector can generate different target pulses for
  multiple syllables at almost no additional computational cost during
  runtime, although training time will increase.
\end{itemize}

>>>>

With inputs well outside the space on which a neural network has been
trained, its outputs will be essentially random. In order to reduce
the false positive rate it is necessary to provide negative training
examples that include silence, cage noise, wing flapping, non-song
vocalisations, and perhaps songs from other birds.  Although it will
depend on the makeup of the non-song data, we have found that training
with as low as a 1:1 ratio of non-song to song yields excellent
results on most birds.  These data are also included in our accuracy tests.

@@

\subsubsection{Computing optimal output thresholds}
\label{sec:optimalthresholds}
After the network is trained, outputs of the network for any input are
now available, and will be in (or, due to noisy inputs and imperfect
training, close to) the interval (0, 1). We must choose a threshold
above which the output is considered a positive detection. Finding the
optimal threshold requires two choices. The first is the relative cost
of false negatives to false positives, $C_n$. The second is the
acceptable time interval: if the true event occurs at time $t$, and
the detector triggers at any time $t\pm\Delta t$, then it is
considered a correct detection. Then the optimal detection threshold
is the number that minimises $\textrm{[false positives]}
+C_n\cdot\textrm{[false negatives]}$ over the training set, using the
definitions of false positives and negatives given in
Section~\ref{sec:accuracy}. Since large portions of the cost function
are flat, we use a brute-force linear search, which requires fractions of a
second. For the results presented here, we have used
$\Delta t=10$ ms, and arbitrarily set $C_n=1$.

@@

We define the accuracy of the network based on its classification
performance per frame. In order to avoid the apparent problem of every
non-detected non-syllable counting as a true negative, we also tried
defining accuracy on a per-song basis, such that a song without the
target syllable counted as a single true negative.  Computing the
optimal output thresholds on a per-frame basis resulted in higher
thresholds and thus a lower false-positive rate, with minimal
consequences to the false-negative rate, while also providing a valid
definition of false-positive rate for data streams that had not been
segmented into song-sized chunks and thus allowing easy interpretation
of false-positive rates from calls, cage noise, etc.

@@

We evaluate the time taken from the presentation of each instance of the target
syllable to the firing of the detector's TTL pulse---for example, if the target trigger point with respect to the aligned songs is at 200 ms, and for a given presentation of the song the detector fires at 203 ms, we take the latency on that trial to be 3 ms.

While playing the
audio test file from any audio playback device, we used the TTL output from
the ground-truth channel of the audio output as the
trigger pulse for an oscilloscope, and compared it to the TTL pulse
produced by the detector, which sees only the birdsong
channel of the audio file. For this purpose we used a pulse generator
(Philips PM 5715, with a listed latency of 50 ns, jitter of $\leq
0.1\%$ or 50 ps, whichever is greater) to widen the detector's output
spike to a number much larger than the jitter ($\sim 100$ ms).  This
obviates pulse length variability in the output device by essentially
discarding the falling edge of the output pulse.  The oscilloscope is
then set to averaging mode (128-trigger average) in order to collect
timing data. The canonical signal is the trigger at $t=0$, and the
average of the detector's detection events will be seen as a
low-to-high transition with form approximating the cumulative
probability distribution function (CDF) of the detector's output in
response to the chosen song event, with individual detection events visible as steps in this curve.

Mean latency is then given as the average time between the 
canonical signal and the corresponding detection event. 
It is a helpful number, but not a critical one, since in zebra finch a
detector with high but constant latency can often be trained to
trigger at a point somewhat before the true moment of interest (for example, if triggering should occur at the very beginning of a syllable, the detector's time window may include previous syllable).  Often more
important is the variability in the
latency?  We define jitter as the standard deviation of the latency.

@@

We have used this detector for song alignment and feedback experiments
in 5 behaving birds, and for offline analysis on various others.  For
simplicity we present performance on 6 randomly chosen points in one
bird's song, but the results presented here are representative of
real-world performance in our lab.\marginpar{Ok?}

@@

@@

This syllable detector is appropriate for zebra finch song, and
although our tests were carried out on songs from that species, it is
also likely to work well for Bengalese finches due to their similarly stereotyped syllables.  It offers the
following benefits:
\begin{itemize}
\item The detector is accurate. False negative and false positive
  rates can be well under 0.5\% and 0.01\% respectively, and trading
  these two numbers off against each other is through a single
  relative-cost parameter.
\item Latency is generally under a millisecond, with jitter around 2
  ms.
\item Works on a wide range of target syllables using the default
  values described here, generally eliminating the need for
  hand-tuning.
\item Runs fast enough for syllable-modification experiments on
  inexpensive consumer-grade hardware, although we recommend that the
  training phase be run on a fast desktop system with 32 GB of RAM.
\item A single detector can generate different target pulses for
  multiple syllables at almost no additional computational cost during
  runtime, although training time will increase.
\end{itemize}
